Typing a linear \picalc

### 2020-03-27 paper/paper.tex
Add a balanced predicate

% Fields
\newcommand{\op}[3]{#1 \; \field{\coloneqq} \; #2 \; \field{\cdot} \; #3}
\newcommand{\li}{\field{\ell_i}}
\newcommand{\lo}{\field{\ell_o}}
\newcommand{\lz}{\field{\ell_{\o}}}
\newcommand{\lio}{\field{\ell_{\#}}}

@@

\begin{figure}[h]
\begin{equation}
\begin{aligned}
  &\lz                    &:{} &                      &        & C \\
  &\li                    &:{} &                      &        & C \\
  &\lo                    &:{} &                      &        & C \\
  &\op{\_}{\_}{\_}        &:{} &                      &        & C \to C \to C \to \Set \\
  &\field{\cdot-join}     &:{} &                      &        & \type{\exists} \lio . \; \op{\lio}{\li}{\lo} \\
  &\field{\cdot-compute}  &:{} &\forall y z           & \to \; & \type{DEC} \; (\type{\exists} x . \; (\op{x}{y}{z})) \\
  &\field{\cdot-unique}   &:{} &\forall \{x x' y z\}  & \to \; & \op{x'}{y}{z} \to \op{x}{y}{z} \to x' \equiv x \\
  &\field{\cdot-unique^l} &:{} &\forall \{x y y' z\}  & \to \; & \op{x}{y'}{z} \to \op{x}{y}{z} \to y' \equiv y \\
  &\field{\cdot-id^l}     &:{} &\forall x             & \to \; & \op{x}{\lz}{x} \\
  &\field{\cdot-comm}     &:{} &\forall \{x y z\}     & \to \; & \op{x}{y}{z} \to \op{x}{z}{y} \\
  &\field{\cdot-assoc}    &:{} &\forall \{x y z u v\} & \to \; & \op{x}{y}{z} \to \op{y}{u}{v} \to \type{\exists} w . \; (\op{x}{u}{w} \times \op{w}{v}{z})
\end{aligned}
\end{equation}
\caption{Quantifier algebra $\Quantifier_C$ algebra on a partial commutative monoid with special elements $\ell_i$, $\ell_o$ and $\ell_\#$.}
\label{capabilities}
\end{figure}

@@

>>>>

% Fields
\newcommand{\op}[3]{#1 \; \field{\coloneqq} \; #2 \; \field{\cdot} \; #3}
\newcommand{\li}{\field{\ell_i}}
\newcommand{\lo}{\field{\ell_o}}
\newcommand{\lz}{\field{\ell_{\o}}}
\newcommand{\lio}{\field{\ell_{\#}}}
\newcommand{\Balanced}{\field{Balanced}}

@@

\begin{figure}[h]
\begin{equation}
\begin{aligned}
  &\lz                    &:{} &                      &        & C \\
  &\li                    &:{} &                      &        & C \\
  &\lo                    &:{} &                      &        & C \\
  &\lio                   &:{} &                      &        & C \\
  &\op{\_}{\_}{\_}        &:{} &                      &        & C \to C \to C \to \Set \\
  &\field{\cdot-join}     &:{} &                      &        & \op{\lio}{\li}{\lo} \\
  &\field{\cdot-compute}  &:{} &\forall y z           & \to \; & \type{DEC} \; (\type{\exists} x . \; (\op{x}{y}{z})) \\
  &\field{\cdot-unique}   &:{} &\forall \{x x' y z\}  & \to \; & \op{x'}{y}{z} \to \op{x}{y}{z} \to x' \equiv x \\
  &\field{\cdot-unique^l} &:{} &\forall \{x y y' z\}  & \to \; & \op{x}{y'}{z} \to \op{x}{y}{z} \to y' \equiv y \\
  &\field{\cdot-id^l}     &:{} &\forall x             & \to \; & \op{x}{\lz}{x} \\
  &\field{\cdot-comm}     &:{} &\forall \{x y z\}     & \to \; & \op{x}{y}{z} \to \op{x}{z}{y} \\
  &\field{\cdot-assoc}    &:{} &\forall \{x y z u v\} & \to \; & \op{x}{y}{z} \to \op{y}{u}{v} \to \type{\exists} w . \; (\op{x}{u}{w} \times \op{w}{v}{z})
\end{aligned}
\end{equation}
\caption{Quantifier algebra $\Quantifier_C$ algebra on a partial commutative monoid with special elements $\ell_i$, $\ell_o$ and $\ell_\#$.}
\label{capabilities}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Progress}\label{progress}

\begin{figure}[h]
\begin{equation}
\begin{aligned}
  &\Balanced                &:{} &                      &        & C \to \Set \\
  &\field{Balanced-}\lz     &:{} &                      &        & \Balanced \; \lz \\
  &\field{Balanced-}\lio    &:{} &                      &        & \Balanced \; \lio \\
  &\field{Balanced-\cdot^l} &:{} &\forall \{x y z\}     & \to \; & \Balanced \; x \to \Balanced \; z \to \op{x}{y}{z} \to \Balanced \; y \\
  &\field{Balanced?}        &:{} &\forall x             &        & \type{DEC} \; (\field{Balanced} \; x)
\end{aligned}
\end{equation}
\caption{}
\label{progress-capabilities}
\end{figure}

\todo{scope extension rule}
